\documentclass[darkmode]{dw_playbook}
% bright white computer screen hurting your eyes?  Specify [darkmode] to invert the color scheme.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Playbook Details
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setPlaybook{Nightwatch}
\title{The \playbook}

\setDamage{\deight}
\setMinHitPoints{8}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Document Layout
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% ----------------------------------------------------------
\pageOne
    {
        \names{Evelyn, Ben, Lucas, Mason, Harper, Jackson, Camila, Scarlett, Isaac, Zoey, Julian, Robert, Riley}
    }
    {
        \looks
        \looksOption{EYES}{Unwavering, Hidden, Light-catching Glasses, \\[1mm]\blank{5.8}}
        \looksOption{HAIR}{Clean Cut, Rougeish, Long and Greasy, \\[1mm]\blank{5.8}}
        \looksOption{BODY}{Built, Lithe, Nearly Skeletal, \\[1mm]\blank{5.8}}
        \looksOption{CLOTHES}{Rich, Self-Made, Street Casual, \\[1mm]\blank{5.8}}

        \vspace{1mm}
        \race\\
        \raceOption{Human}
            {When you \important{enter a civilized settlement} you've visited in the past, tell the GM about a criminal that you helped catch last time you were there.  The GM will tell you if they're still seeking revenge.}
        \raceOption{Elf}
            {Nature is not lawless, but it recognizes different laws than that of man.  You may use \important{Throwing Shade} to accuse a GM character of transgressions against nature, even if those transgressions are not represented in the laws of civilized society.}
        \emptySelectable{5}
    }
    {
        \selectable[x]{Enshaden}
            {When you stand in a darkly shaded or lightless place and \important{wrap the darkness around yourself}, you gain a real cloak made of shadows.  This cloak is pocketless, but feels and acts like any regular cloak.  The material will slowly smolder away if exposed to direct sunlight.  If you take the cloak off it falls to the ground, thin as a shadow, and cannot be picked back up.
            \gap
            While wearing this cloak, take +1 ongoing for any roll where you attempt to stay hidden, or to move or act without being seen.}
        \gap
        \selectable[x]{Caped Crusader}
            {Mounted to a brace on your forearm you have a small, modified crossbow which fires a grappling hook attached to a twenty-foot long rope.  The rope is load bearing, allowing you to dangle, climb, or swing from it.  You may dislodge the hook from any surface with a quick flick of the rope.
            \gap
            The whole apparatus can collapse down to stay tucked away and mostly discreet.  Unlike a normal crossbow it cannot fire bolts.  Reloading takes a minute of concentration.  You cannot use it while holding a shield or weapon with that arm.}
        \selectable[x]{A Slice of Moonlight}
            {When you \important{bare your blade to the moonlight}, the light gathers on the exposed metal and illuminates the blade.  Gain 1 hold.  Spend this hold to Volley the light as if you had thrown the blade itself.  On a 7-9 you cannot choose to reduce your ammo.  If you sheath or hide the blade, the light dissipates and you lose all hold.}
        \gap
        \selectable[x]{Throwing Shade}
            {When you have dirt on a GM character and \important{publicly accuse them of crimes or misdeeds}, roll+CHA.  On a hit the GM chooses one:
            \gapSm
            \opt{Make up a bad excuse to be somewhere else, then flee.}
            \gapSm
            \opt{Get defensive and focus their attention on you.}
            \gapSm
            \opt{Own up to their deviant ways without a hint of remorse.}
            \gap
            On a 10+, take +1 forward against them.  On a miss, they mock your delusions: take -1 forward against them.}
        \gap
        \selectable[x]{Creature of the Night}
            {Whenever you \important{Take Watch at night}, take +1 forward on the roll.  While on watch you are Enshaden and difficult to see.  On a 10+, it is impossible to get the drop on you.}
    }

% ----------------------------------------------------------
\clearpage
~

\pageTwo
    {
        \bonds
        \bondOption{\blankName~has earned my trust, for they truly know right from wrong.}\\
        \bondOption{\blankName~knows about my past life, and could use those secrets against me.}\\
        \bondOption{If I let them stray from my watch, \blankName~would harm an innocent person.}\\
        \bondOption{A long time ago, I saved \blankName~in a bad part of town, I wonder if they remember.}\\
        
        \vspace{2mm}
        \blank{5.8}\\
            
        \blank{5.8}\\
            
        \blank{5.8}

        \vspace{1mm}
        \alignment
        \alignmentOption{Good}{Put yourself in danger to catch a crook.}
        \gap
        \alignmentOption{Lawful}{Pursue justice above all other virtues.}
        \gap
        \alignmentOption{Evil}{Go to any lengths to stop evil.}

        \emptySelectable{5}
        \gear
        \adventuringGear
        \gearOption{\important{Leather Armor} (1 armor, \tag{worn}, 1 weight)}
        \gearOption{\important{Arm-mounted Grappling Bow} (\tag{worn}, 1 weight)}
        \gap
        \instruction{Choose your armament:}
        \gap
        \gearOptionSelectable{\important{Short Sword} (\tag{close}, 1 weight)}
        \gearOptionSelectable{\important{Rapier} (\tag{close}, \tag{precise}, 1 weight)}\\
        \instruction{Choose two:}
        \gap
        \dungeonRations[s]
        \gearOptionSelectable{\important{Throwing Daggers} (3 uses, \tag{thrown}, \tag{near}, 0 weight)}
        \gearOptionSelectable{\important{Antitoxin} (3 uses, 0 weight)}
    }
    {
        \selectable{Plenty of Pockets}
            {Your cloak of shadows gets some small pockets.  When the cloak disappears the items in the pockets disappear with it, but are found in the same pocket next time you put it on.}
        \gap
        \selectable{Glider}
            {While Enshaden, you may fan out your cloak like a set of wings and glide through the air.}
        \gap
        \selectable{A Lash of Firelight}
            {You may use a fire to gather light on your blade, just as you would have with moonlight.}
        \gap
        \selectable{Word Says You're\\Looking For Me}
            {When you \important{put out word to the criminal underbelly} that there’s someone you want to meet, roll+CHA.  On a 10+, they’ll set up a meeting with you.  On a 7–9 you’ll have to settle for an associate or lackey, or the meeting comes with strings attached, your call.}
        \selectable{Henchmen}
            {When you’re outnumbered by two or more you deal +2 damage with \important{Hack and Slash}.}
        \gap
        \selectable{Turning Over A New Leaf}
            {When you \important{Recruit} some help, you have the option to skip the roll.  If you do, you are guaranteed an applicant who is capable and willing to work for cheap, but is also a former criminal looking for a second chance.  They’ll carry old baggage to deal with, and after a lifetime of crime you might find their old habits die hard.}
        \gap
        \selectable{Limit Break}
            {When you \important{gather light on your blade}, you gain 2 hold.  While you have light on your blade, deal an additional +1 damage.}
        \gap
        \selectable{A Blade In The Darkness}
            {When you \important{fight in a dark place}, Gain +1 armor if you are Enshaden, and +1 armor if you have light on your blade.  If both are active, opponents are easily confused by your movements.}
    }
    {
        \selectable{Get Over Here}
            {You gain a second grappling hook, constructed as an outward-facing claw.  When you \important{fire the claw at a grabbable object}, roll+DEX.  On a 10+ that thing is safely snatched by the claw and knocked free for retrieval.  On a 7-9, you latch onto the object, but you’ll have to engage in tug-of-war to get it loose.
            \gap
            When you \important{fire your grappling hook at a \tag{large} or \tag{huge} creature}, roll+STR.  On a hit you can climb and swing from the rope as if it were hooked to a piece of the environment.  On a 10+ you don’t lose control if the creature flails around with you dangling from them.}
        \gap
        \selectable{Wings}
            {\replaces{Glider}
            Your cloak is modified for greater agility in the air.  In addition to gliding you can perform all sorts of aeriel acrobatics, including flapping the cloak to gain speed and a little altitude.}
        \selectable{Shadow Walker}
            {When you’re Enshaden and you \important{walk into a dark shadow or lightless area}, you disappear into the darkness and are gone, even if there’s nowhere you could go.  You reappear a moment later from any other shadow or lightless area \tag{near} where you entered.}
        \gap
        \selectable{Trance}
            {\replaces{Limit Break}
            When you gather light on your blade you gain 3 hold.  While you have light on your blade, gain +1d4 damage.}
        \gap
        \selectable{Shake Off Cape}
            {If you take damage while Enshaden and \important{throw off your cloak with a flourish}, you ignore the damage.  Whatever was meant to hit you hits your cloak instead.}
    }

% ----------------------------------------------------------
\clearpage
~

\pageThree
    {
        \advancedMovesCont
    }
    {
        \selectable{Warden}
            {When you \important{return to a civilized place where an ally has an Outstanding Warrant}, and you make a show of leading that character around as if they are your prisoner, you both roll+CHA and use the best result  On a 10+, word has spread both about their capture and your presence as their captor, and everyone believes the situation is under control.  On a 7-9, word of your deeds have spread, but the GM chooses a complication:
            \gapSm
            \opt{The local constabulary will come around to assess the situation for themselves.}
            \gapSm
            \opt{Someone will come asking for recompense for prior damages.}
            \gapSm
            \opt{The town still doesn’t want them around, and would prefer you leave quickly.}
            \gap
            When you \important{return to a civilized place with a notorious criminal or wrongdoer in your arrest}, the town celebrates your victory.  In addition to reaping the rewards for their capture, you may Carouse without spending the initial 100 coin.}
        \selectable{Dynamic Duo}
            {You’ve gained a sidekick in the form of a child or young adult.  Why are you willing to take them in as your ward and apprentice and let them join you on your adventure.  Choose one of the following which describes them best:
            \gap
            \opt{Orphaned and lost, but with great resilience and courage.\\
            Con: +1.  Cha: -1.  Int: -2.\\
            16 max HP.  D8 damage.  8 Load.}
            \gap
            \opt{Strange, awkward, and possessed with insight and understanding.\\
            Wis: +1.  Str: -1.  Cha: -2.\\
            12 max HP.  D6 damage.  6 Load.}
            \gap
            \opt{Unwittingly eager and gangly, with genius to match enthusiasm.\\
            Int: +1.  Con: -1.  Str: -2.\\
            10 max HP.  D4 damage.  4 Load.}
            \gap
            \opt{Ferocious and uncontrollable, yet stalwart and devoted.\\
            Str: +1.  Dex: -1.  Wis: -2.\\
            14 max HP.  D10 damage.  10 Load.}
            \gap
            \opt{Candid and naive, able to make friends in any situation.\\
            Cha: +1.  Wis. -1.  Con: -2.\\
            8 max HP.  D6 damage.  6 Load.}
            \gap
            Treat your sidekick as a playable character in your control.  They do not choose a playbook, gain experience, or level up.}
    }
    {
        ~
    }

% ----------------------------------------------------------
% Hey there fellow playbook creator!  Thanks for trying out this latex project.  Formatting documents is a tough gig, and even with the tools arranged here I'm sure you'll go through a few headaches.  Feel free to reach out if you've hit a wall.

% I'm only going to ask you for one thing: please keep this final page intact.  Help other players and designers find this resource as well.  While you're at it, if you're making your own playbook you probably have a drivethru or itch.io account, if not your own website, right?  Add a link to it here!

% Thanks again, and happy designing!

\clearpage
~

\resourceLinks
    {
        % link to your stuff here!
        % ex:
        % More awesome playbooks can be found at at:\\\url{https://itch.io/myOtherCreations}
    }
\end{document}