\documentclass[darkmode]{dw_playbook}
% bright white computer screen hurting your eyes?  Specify [darkmode] to invert the color scheme.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Playbook Details
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setPlaybook{Powder Mage}
\title{The \playbook}

\setDamage{\dsix}
\setMinHitPoints{4}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Document Layout
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% ----------------------------------------------------------
\pageOne
    % any text that appears betweeen the top banner and the stats
    {
        \names{Olivia, Jack, Oscar, Benjamin, Ava, Lilly, Finley, Reuben, Emily, Isabel, Mia, Ollie, Ezra, Roman, Poppy, Florence, Holly}
    }
    % left-hand column (looks, race)
    {
        \looks
        \looksOption{EYES}{Goggled, Quick, or Ponderous}
        \looksOption{HAIR}{Singed, Slicked, or Ignored}
        \looksOption{HANDS}{Nimble, Scarred, or Steady}
        \looksOption{CLOTHES}{Practical, Business oriented, or Blacksmith’s leathers}

        \vspace{1mm}
        \race\\
        \raceOption{Human}
            {When you \important{burn a pinch of powder} to impress or dazzle onlookers, the sparks take on whatever shapes, colors, and movement you wish.}
        \raceOption{Dwarf}
            {When you \important{burn a pinch of powder} to impress or dazzle onlookers, the smoke takes on whatever shapes, colors, and movement you wish.}
        \diyMove{5}
        \gapSm
        \separator{5.8}
        \gap
        \move[x]{Need a Light?}
            {When you \important{snap your fingers}, a small flame appears at the tip of your thumb.  You, personally, cannot be harmed by this flame.}
    }
    % Starting Moves
    {
        \move[x]{Blunderbuss}
            {You have a custom-made flintlock gun entirely designed, tested, and assembled by you.  Your blunderbuss has the tags \tag{reach}, \tag{near}, \tag{reload}, \tag{two-handed}, and \tag{loud}.  If anyone besides yourself attempts to use your gun, they deal with the tags \tag{dangerous} and \tag{awkward}.  
            \gap
            The construction is simple, yet durable and able to withstand punishment similar to a martial weapon.  If your blunderbuss gets lost or destroyed you can craft a replacement.  This process takes one month of labor and 50 coins.  Each additional 50 coins spent reduces the construction time by one week, down to a minimum of one week of labor.
            \gap
            Your blunderbuss will accept any object of approximately correct size and shape as a slug (you generally carry a couple iron balls in your pockets for this purpose), and as a result you will always have slugs readily available.  Instead of tracking projectiles, all rules involving ammo apply to your black powder reserves instead.  Replacement powder can be purchased, where appropriate, for 15 coin per cask, or 3 coin per ammo (max 5 ammo per cask).}
        \gap
        \move[x]{Environmental Hazards}
            {When you Discern Realities, you may ask the following questions:
            \gapSm
            \opt{Are there explosives or incendiaries nearby?}
            \gapSm
            \opt{Who here has a short fuse or is about to blow?}}
        \move[x]{Arcane Grenades}
            {When you \important{spend an uninterrupted hour with your tools}, remove one charge of black powder to construct any arcane grenade from the list. These grenades are inherently \tag{volatile}, and you wisely only ever carry one at a time.
            \gapSm
            \opt{\important{Earthbreaker}: \tag{dangerous}, \tag{forceful}, and \tag{loud}.  2d6 damage in a 20-foot radius.  A rather standard, but powerful explosion that rattles stone and sends debris flying.}
            \gapSm
            \opt{\important{Dragon’s Fire}: \tag{dangerous}, and \tag{incendiary}.  1d6 + 1d4 damage in a 10-foot radius, coating everything inside the blast with flame.}
            \gapSm
            \opt{\important{Thunder Snap:} \tag{stun}, \tag{blinding}, and \tag{deafening}.  1d4 damage in a 20-foot radius.  Minimal impact, but the extraordinarily interruptive boom will temporarily blind and deafen anyone in range.}}
        \gap
        \move[x]{Thou Shalt Count To Three}
            {When you \important{throw an arcane grenade}, roll+DEX.  On a 10+ the grenade lands exactly where you want it to go, and the fuse goes off at exactly the right time.  On a 7-9, choose one:
            \gapSm
            \opt{You still hit your target, but you involve some collateral as well.  The GM will tell you which characters and objects were accidentally caught in the blast.}
            \gapSm
            \opt{The grenade lands exactly where you wanted, but to make the throw you had to expose yourself to additional danger.}}
    }

% ----------------------------------------------------------
\clearpage
~

\pageTwo
    % left-hand column (bonds, alignment, gear)
    {
        \bonds
        \bondOption{\blankName~is too uptight, I should teach them something about excitement.}\\
        \bondOption{\blankName~likes a show of force, I could impress them easily.}\\
        \bondOption{\blankName~doesn’t trust my work, but I can prove I’m in control.}\\
        \bondOption{\blankName~has knowledge that I can apply to my work, I must get them to teach me.}\\
        
        \vspace{2mm}
        \blank{5.8}\\
            
        \blank{5.8}\\
            
        \blank{5.8}

        \vspace{1mm}
        \alignment
        \alignmentOption{Neutral}{Don’t be afraid to go bigger.}
        \gap
        \alignmentOption{Lawful}{Keep someone volatile in check.}
        \gap
        \alignmentOption{Chaotic}{Strike sparks just to see what catches fire.}\gapSm
        \diyMove{5}

        \gear
        \gearOption{You carry your \important{Blunderbuss} (\tag{reach}, \tag{near}, \tag{reload}, \tag{two-handed}, \tag{loud}, 1 weight)} 
        \gearOption{An \important{Arcane Grenade} (0 weight)}
        \gearOption{\important{Cask of Black Powder} (5 ammo, 1 weight)}
        \gearOption{\important{Powder Tools} (1 weight)}
        \gapSm
        \separator{5.8}
        \gap
        \instruction{Choose two:}
        \gap
        \dungeonRations[s]
        \adventuringGear[s]
        \gearOptionSelectable{\important{15 coins}}
    }
    % Advanced Moves (2-10)
    {
        \move{Invert the Mechanical\\and the Arcane}
            {Replace your grenade options in Thou Shalt Count to Three with the following:
            \gapSm
            \opt{\important{Void Thumper}: \tag{dangerous}, \tag{ignores armor}, and \tag{arcane}.  3d4 damage in a 20-foot radius.  The explosion makes no sound, produces no force, and is barely visible save for a faint ripple expanding outward from the origin.  The shockwave penetrates all but the thickest walls.}
            \gapSm
            \opt{\important{Snow Globe}: \tag{dangerous}, and \tag{freezing}. 2d6 damage in a 10-foot radius, freezing everything within the blast.}
            \gapSm
            \opt{\important{Astral Vortex}: \tag{stun}, \tag{ignores armor}, and \tag{arcane}.  1d4 damage in a 20-foot radius.  Everything in the blast is sucked inward towards the center by powerful winds.}}
        \gap
        \move{Blackbeard}
            {When you light the fuses attached to your hair and clothes and \important{burst into the scene roaring like a demon of smoke and embers}, roll+CHA.  On a hit, opponents are reluctant to come near you.  On a 10+ you gain +1 forward to Defy Danger.  On a miss, enemies think you're their greatest threat.}
        \gap
        \move{Bellow}
            {When you \important{load your blunderbuss with an extra heap of black powder} instead of a slug, spend one powder.  On your next Volley your blunderbuss belches out a wave of arcane fire.  (The result may differ if your blunderbuss is attuned to an element.  You and the GM decide what changes when you attune.)}
        \gap
        \move{Useful In A Pinch}
            {Attach an axe blade to the barrel or the stock of your blunderbuss.  When you use it to Hack and Slash, treat the gun as a melee weapon with the tags \tag{close}, and \tag{two-handed}.  If it's attuned, add the attunement tag as well.}
        \move{There Is A Fine Line}
            {When your behavior forces an ally to Defy Danger, they gain +1 forward.}
        \gap
        \move{Wreck}
            {When you have enough time and safety with your tools to \important{rig up a demolition charge}, roll+INT and negotiate with the GM over how much powder you’ll have to spend to get the effect you desire (minimum 1).  On a 10+, the demolition goes exactly as planned.  On a 7-9, the GM chooses one or more of the problems below.  On a miss, prepare for the worst.
            \gapSm
            \opt{The blast is weak or placed incorrectly: the result is less than what you wanted.}
            \gapSm
            \opt{It took extra resources to get the job done right: spend 1 additional powder.}
            \gapSm
            \opt{It’s a tricky bit of work: setting up takes extra minutes/hours.}
            \gapSm
            \opt{The blast didn’t go according to plan: put someone or something in danger.}}
        \gap
        \move{Smoke Screen}
            {When you \important{throw a handful of powder into the air and set it aflame}, a black curtain of smoke, too thick to see beyond, hangs behind to burn the eyes and scour the lungs of all inside.}
        \gap
        \move{Can Melt Steel Beams}
            {Everyone caught in a grenade’s explosion must pick either their armor or their shield (their choice) and permanently reduce its armor by 1.  If that item has 0 armor afterward, it gets destroyed.  Anyone caught in the blast with no armor to reduce takes 1d6 additional damage.}
        \gap
        \move{Remote Detonator}
            {When you create an arcane grenade, you also weave a spell onto a mundane item such as a match, a spare fuse, or some flash paper, thereby pairing it to the grenade.  When the two are \tag{near} each other, you can detonate the grenade by setting its paired item on fire.}
    }
    % Advanced Moves (6-10)
    {
        \move{Attune}
            {When you \important{attune your blunderbuss} to a place of great elemental energy, remove any current attunement and add whatever element dominates this location to your blunderbuss’ tags.  The attunement lasts until it is replaced or intentionally removed.}
        \move{Scavenge}
            {When you \important{Make Camp}, add up to two powder to your reserves.  But only if you have space for it in a cask.  When you take time to \important{Recover}, for each day you spend recovering you can completely fill one cask with powder.}
    }

% ----------------------------------------------------------
\clearpage
~

% the third page has empty lines for notes on the left-hand column, and I don't
% leave you any options for changing that up.  Everything you can configure here
% goes into the right hand column.
\pageThree
    % full-width section for an optional title bar.
    {
        \advancedMovesCont
    }
    % two-column section for listing moves
    {
        \move{Between Help And Harm}
            {\replaces{There is a Fine Line}
            When your behavior forces an ally to Defy Danger, they gain +1 forward.  For those allies with whom you share a bond, you may roll+Bond to Aid or Interfere with them, no matter the circumstance.  For friendly GM characters you also may Roll+1 to Aid or Interfere.}
        \gap
        \move{Rocket Jump}
            {\requires{Bellow}
            When you load your blunderbuss with an extra heap of powder instead of a slug and fire it with the muzzle pointed beneath you as you leap, the arcane blast propels you upwards with incredible velocity.  Spend one powder and Roll+DEX.  On a 10+ you soar acrobatically towards your destination.  On a 7-9, pick one:
            \gapSm
            \opt{You fly towards the exact spot you intended.}
            \gapSm
            \opt{You stick the landing, wherever it is.}}
        \gap
        \move{Torgue Manufacturing}
            {When you create an arcane grenade, you use the leftover components to create a single arcane slug.  This slug can be fired as a regular Volley, is always consumed when used, and only detonates on impact.  The slug’s tags reflect the tags of the grenade itself, but the area of effect and damage are as follows:
            \gapSm
            \opt{Earthbreaker: 2d4 damage, 5-ft radius.}
            \gapSm
            \opt{Dragon’s Fire: 1d4 damage, 1-ft.}
            \gapSm
            \opt{Thunder Snap: No damage, 10-ft.}
            \gapSm
            \opt{Void Thumper: 1d6 damage, 5-ft.}
            \gapSm
            \opt{Snow Globe: 1d6 damage, 3-ft.}
            \gapSm
            \opt{Astral Funnel: No damage, 10-ft.}}
        \move{Holding A Thermal Detonator}
            {When you \important{try to swing a tense situation in your favor by showing off a grenade}, roll+CHA.  On a hit the NPCs involved:
            \gapSm
            \opt{Admire your brazen tactics and give you what you want.}
            \gapSm
            \opt{They’re over it.  You get your way, but the relationship has soured.}
            \gapSm
            \opt{Panic.  All hell breaks loose.}
            \gap
            On a 10+ take +1 forward to whatever happens next.  On a miss, take -1 forward, and you’ll probably need to use that grenade to get you out of this mess.}
        \gap
        \move{Uncertain Until Observed}
            {When you create an arcane grenade, write down two grenades from your available options.  You don’t need to choose which of the two you created until the grenade explodes.
            \gap
            Additionally, choose one grenade from \important{Invert The Mechanical And The Arcane} and add it to the list of grenades you can make.  If you already took Invert the Mechanical and the Arcane, choose a grenade from the original list and add it to the list of grenades you can make.}
        \gap
        \move{Useful In Most Situations}
            {\requires{Useful in a Pinch}
            Reinforce your blunderbuss with protective plating.  You gain +1 armor whenever you wear or hold it.  It doesn’t cover much of your body at any time, but whenever it makes sense you may use your blunderbuss as a shield without any worry of it getting damaged.}
    }
    % and/or a single-column section if you want to use the third page for
    % something with a different layout than before
    {
        ~
    }

% ----------------------------------------------------------
% Hey there fellow playbook creator!  Thanks for trying out this latex project.  Formatting documents is a tough gig, and even with the tools arranged here I'm sure you'll go through a few headaches.  Feel free to reach out if you've hit a wall.

% I'm only going to ask you for one thing: please keep this final page intact.  Help other players and designers find this resource as well.  While you're at it, if you're making your own playbook you probably have a drivethru or itch.io account, if not your own website, right?  Add a link to it here!

% Thanks again, and happy designing!

\clearpage
~

\resourceLinks
    {
        % link to your stuff here!
        % ex:
        % More awesome playbooks can be found at at:\\\url{https://itch.io/myOtherCreations}
    }
\end{document}